Response to reviewers

### 2025-07-04 src/docs_paper-jtb/revisions.Rmd
Soften reply

The goal of Bayesian optimisation (BO) is to find the maximum of a (black box) function.
For this reason, we do not see BO as a competitor to algorithms (like ours) intended to perform Bayesian inference.
(One could imagine using BO to optimise the hyperparameters, however it would be preferable to use gradients [as they are available].)

>>>>

Our understanding is that the goal of Bayesian optimisation (BO) is to find the maximum of a (black box) function, rather than to perform Bayesian inference.
One could imagine using BO to optimise the hyperparameters, however it would be preferable to use gradients as they are available.
